### Load Packages

```{r}
install.packages("dataRetrieval")
install.packages("dplyr")

library(dataRetrieval)
library(dplyr)
```

## USGS streamgages - Arizona

-   Data source: USGS
-   Timeframe: Full period of record

```{r}
AZ_streamgages<- dataRetrieval::whatNWISsites(stateCd = "AZ", #Only sites in AZ
                            parameterCd = "00060",  #discharge
                            service="dv") # daily value

sites <- filter(AZ_streamgages, site_tp_cd %in% c('ST')) #only sites that are a Stream <- this removes most streamgages with anthropogenic impacts on the basin
sites <- sites[,-c(1,4,7,8)] #remove unwanted columns
colnames(sites) = c('Site_Num', 'Station_Name', 'Latitude', 'Longitude')
```

-   Get period of record for each gauge

-   Select Years: Check number of days for each year (only keep those with \>335 days/yr)

-   If that gauge has \>10 selected years, it is added to our study list

-   Create dataframe for each state with USGS streamgage #, Lat, Long, Number of selected years, list of all applicable years
